MSF_Groupwork-NBA_shotlog

### 2016-10-16 MSFGroupwork-NBAHotHand.Rmd
Removed all "HEAD"

@@

```{r, include=FALSE}
#change distance level to numeric type for correlation test function
distance_level$Var1 <- as.numeric(distance_level$Var1)
distance_level$Var1 <- distance_level$Var1 * 0.1 - 0.1 #to keep the distance point as it is

@@

#Calculate shooting accuracy for each distance
shooting_distance_level$Accuracy <- round(shooting_distance_level$SCORED / shooting_distance_level$Freq, 4)
```

@@

  Analysis has also produced a correlation test. If the analysis included **all** of the data points for every distance, the correlation result would be as follows:  
  There was strong negative correlation found between the shooting distance and shooting accuracy. The Pearson’s correlation coefficient for the relationship between the variables Shooting Distance and Shot Accuracy was r(446) = -0.87, p < .05, as part of level of significance (p = .05).
```{r, include=FALSE}
#change distance level to numeric type for correlation test function
shooting_distance_level$Var1 <- as.numeric(shooting_distance_level$Var1)
shooting_distance_level$Var1 <- shooting_distance_level$Var1 * 0.1 - 0.1 #to maintain distance data point as it is

@@

##Hot Hand Theory
###Introduction
  The specific analysis aims to show the effect of the 'hot hand theory' on NBA players. The analysis is aimed to establish whether there are  the hypothesis that a shooter with a hot hand will have shots that are dependent of one another. If the shooter makes his first shot, the probability of making his next shot is higher.

>>>>

#change distance level to numeric type for correlation test function
distance_level$Var1 <- as.numeric(distance_level$Var1)
distance_level$Var1 <- distance_level$Var1 * 0.1 - 0.1 #to keep the distance point as it is

@@

@@

#Calculate shooting accuracy for each distance
shooting_distance_level$Accuracy <- round(shooting_distance_level$SCORED / shooting_distance_level$Freq, 4)

#change distance level to numeric type for correlation test function
shooting_distance_level$Var1 <- as.numeric(shooting_distance_level$Var1)
shooting_distance_level$Var1 <- shooting_distance_level$Var1 * 0.1 - 0.1 #to maintain distance data point as it is
```

@@

  Analysis has also produced a correlation test. If the analysis included **all** of the data points for every distance, the correlation result would be as follows:  
  There was strong negative correlation found between the shooting distance and shooting accuracy. The Pearson’s correlation coefficient for the relationship between the variables Shooting Distance and Shot Accuracy was r(446) = -0.87, p < .05, as part of level of significance (p = .05).
```{r, include=FALSE}

@@

##Hot Hand Theory
###Introduction
  The analysis aims to investigate whether the effect of the 'hot hand theory' is valid based on the given dataset. The 'hothand theory' states that if the shooter makes his first shot, the probability of making his next shot is higher.

  The specific analysis aims to show the effect of the 'hot hand theory' on NBA players. The analysis is aimed to establish whether there are  the hypothesis that a shooter with a hot hand will have shots that are dependent of one another. If the shooter makes his first shot, the probability of making his next shot is higher.
